---
title: "Lab 08 - University of Edinburgh Art Collection"
author: "Yuxin Xie"
date: "3/3/2025"
output: github_document
---

## Load Packages and Data  

First, let's load the necessary packages:  

```{r load-packages, message = FALSE}
library(tidyverse) 
install.packages("skimr")
library(skimr)
```

Now, load the dataset. If your data isn't ready yet, you can leave `eval = FALSE` for now and update it when needed.  


```{r load-data, message = FALSE, eval = FALSE}
# Remove eval = FALSE or set it to TRUE once data is ready to be loaded
uoe_art <- read_csv("data/uoe-art.csv")
```

## Exercise 9

##Let's start working with the **title** column by separating the title and the date:  

```{r separate-title-date, error = TRUE}
uoe_art2 <- uoe_art %>%
  separate(title, into = c("title", "date"), sep = "\\(") %>%
  mutate(year = str_remove(date, "\\)") %>% as.numeric()) %>%
  select(title, artist, year, link)  
```



## Exercise 10  

*Write your answer here.*  

Feel free to add code chunks as needed. Don't forget to label your code chunk.


## Exercise 11  


*Continue with the same structure as above.*

You're doing great—keep going! Follow the same format and add your response below.  


## Additional Exercises  

Almost there! Keep building on your work and follow the same structure for any remaining exercises. Each exercise builds on the last, so take your time and make sure your code is working as expected.  
